\section{INTRODUCTION}
\par In modern society, watching movies is becoming a central part of consumer culture which makes the great earning of investments about movies. However, how to evaluate the reasonability of investments becomes an important problem for investors. Owing to complex movie markets,  the success of a movie is closed related to audience reactions, screenplay, movie types and famous cast and directors.  Before a movie releases, we cannot guarantee it can be popular or not.
\par In recent years, with the heat of the movie market, large amounts of money pour into movie industry. Investments about movies consist of cast's and directors' salary,  movie itself production. advertising fees etc. Actors and directors salary occupies a large proportion in cost of movies. The immaturity of the Chinese film market itself leads to a high-risk, high-reward investment environment.Many investors determine the investment prospects of the film is based on the recent case of the same type of movie, but they do not have in the analysis of the case from the aspect of artistic creation (such as the type of film plot, actor and director of skill etc.) the ability to summarize experience of selling products, most will eventually reduced to the accumulation of the casting and some business element. This is a lot of investment some important reasons can be started the project and ultimately a huge loss.
\par Recently, the group acts of "fans" do not only create a great social effect, but also produce a huge economic benefit. Without bankable stars the film script aroused no interest. In order to pursue high profit, the usual way is to use a large number of "celebrities" to promote the box office through the fan effect but only a few were success. But it has caused the soaring star worth, the consequent increase in production costs. The reason is that in spite of massive "fans", the degree of match between fans and movies is the most important factor affecting the box office. Another is that box office is decided by actors, scripts, publicity, release schedule and other aspects, actors' contribution to the movie cannot be equal to box office. The lack of an effective quantitative method to assess the creative record of the box office contribution prevent investors from assess the investment star's rationality.
\par Besides the cost of production about movies, investors are concerned about box-office revenue. The research on movies maily focuses on movie box-office prediction\cite{marshall2013forecasting,basuroy2003critical,asur2010predicting}. They use linear regression, neural networks\cite{sharda2006predicting} and other models to predict box office more accurately by constructing multiple features, for instance, Google \cite{panaligan2013quantifying} uses search, ad click data, and line rows to predict box office and gets 94\% accuracy. Sentiment analysis in movie reviews \cite{manek2017aspect,kiritchenko2014sentiment,pang2008opinion} is another aspect to do some analysis in movies and many experiments\cite{gemser2007impact,joshi2010movie} prove that reviews data can improve box-office predicting accuracy.
\par In recent years, the research on movie mainly focuses on the construction of user-oriented movie recommendation system\cite{diao2014jointly,tang2015user}. However, those work are too simple to do some analysis on the components of revenue further. Generally speaking, investors are anxious to have a tool or a platform to do a more intuitive analysis of a movie's return on investment. In general, an investor-oriented movie analysis platform is for the Chinese movie market, providing an investor-oriented integrated emotional analysis, box office prediction, actor evaluation, box office contribution analysis of the analysis of the box office analysis of the movie, focusing on the protagonist, director, audience impact on the box office.
\subsection{Solutions and Challenges}
As methods developments in machine learning especially text mining increasing rapidly, much data mining techniques are proved to be effective method in both natural language process (NLP) and deep learning (DL). Social-respected analysis system(\system) is an end-to-end platform which aim to integrate social data of movies when analysing their investment value and potential future. \system makes great contribution in mining movie industry data from three points of view. We summarized it the actress played by actor, box-office pay back for investors, and sentiment reflect by audience. We proposed target-depend sentiment analysis for sentiment side, dynamic predition for box-office and finally the heteogenous network for investor. The key problem \system focused on are listed below.
\newtheorem{difficulties}[theorem]{difficulty}
\begin{difficulties}
Given a comment, how do you analyze the names and emotions mentioned in this comment? \end{difficulties}
\par The existing sentiment analysis of movie reviews rarely seldom further analyzes the sentiment of the commentators. In social media, audiences may show different affective tendencies toward different protagonists of the movie, where traditional short text sentiment analysis can not capture these sentiments. To solve this problem, \system provides an object-oriented commentary sentiment analysis that performs named entity recognition and sentiment classification for each comment to more accurately capture the viewer's preference for a particular director (actor) of a particular movie.
\begin{difficulties}
How to quantify the director's contribution to the box office?
\end{difficulties}
\par Director (starring) contribution to the box office refers to the audience for the expectations of one or a few people to generate consumer spending movie tickets, analyze the contribution of a box office contribution to help get the actual business director or director value. In the analysis of the box office data, it is difficult to quantify the actual box office revenue of every star / director in a movie. There is also a lack of analysis of related modules in the existing commercial movie analysis system.
\system provides a dynamic analysis module that accounts for the share of the box office's contribution, not only to quantify the box office's contribution but also to analyze the changes in the commercial value of a master before and after the release of the movie through changes in contributions over time.
\begin{difficulties} Joint value evaluation and replacability among actors.\end{difficulties}
\par Since effect of an actor suffer multi uncertainties and how to make a joint-evaluation of actor impact is a big question. A lot of method focus on giving linear weight for each factor. But this weight might change and impractical when goal of analysis changing. In \system, we mining joint value based on relationship among actors using heterogeneous network. Qualifying similarity and measuring increase of influence by co-star of two specific actor for target movie show great power on practicability of the system which enhance availability and effectiveness of \system a lot.
\begin{difficulties}
In which way the unstructured data cooperate with structured data?
\end{difficulties}
\par It is a  problem how much effect by just using reviews(the unstructured data) or combine many other factor in analysis. We see that integrate sentiment help to prediction and investment, considering textual data an intensifying factor for attribute of movie itself. Whether the effect existing in each other if we analyse the synergy effects is unknown. To solve this problem, constrained network and iterative algorithm have been proposed to capture effect between the two kinds of data.

\subsection{Roadmap}
The rest of this paper is organized as follows, Section \ref{sec:overviw} presents an overview of \system. In section \ref{sec:sent} we further study name entities recognition based on disambiguation and then describe how \system extract target-dependent sentiments and analyse changeable trend on sentiment. Section \ref{sec:impact} presents dynamic impact of leader creators based on both sentiments and self attributes. In section \ref{sec:predict} present the core value of system by phased prediction of movies which helps to maximum box-office based on reasonable investments now and future. Section \ref{sec:evo} presents system evaluation as well as the case study. In section \ref{sec:related}, we introduce the related work. Finally, Section \ref{sec:conclu} concludes the paper. 